\propertitle

### 2019-07-11 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T13:15:49+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Now consider the related question: What is the activity $\yA_{t}$ of the
full network at some specific time bin $t$? If we don't know the exact
sequence of activities during the recording then we don't know $\yA_{t}$;
if we know the frequency distribution $\yF$ of the activity levels, then
our probability for $\yA_{t}$ is $\yFF_{\yA_{t}}$, out of combinatorial
reasons. But if we are also uncertain about $\yF$, with
probability~\eqref{eq:density_F}, then our probability for $\yA_{t}$ by
marginalization is
\begin{equation}
  \label{eq:probability_AT}
  \pf(\yA_{t} \| \yD \yI) =
  \smallint \yFF_{\yA_{t}}\;   \pf(\yF \| \yD \yI)\;\di\yF;
\end{equation}
our probability distribution for $\yA_{t}$ is thus simply the mean
$\int \yF\; \pf(\yF \| \yD \yI)\;\di\yF$.

@@

If the probability density $\pf(\yF \| \yD \yI)$ is extremely peaked at some
frequency distribution $\yFm$, it can be approximately treated as a delta
density,
\begin{equation}
  \label{eq:approx_delta_pF}
  \pf(\yF \| \yD \yI)\;\di\yF \approx \delta(\yF-\yFm)\;\di\yF,
\end{equation}
and consequently the probability for the activity at bin $t$, by
\eqn~\eqref{eq:probability_AT}, is simply the mode $\yFm$ itself:
\begin{equation}
  \label{eq:approx_delta_pA}
  \pf(\yA_{t} \| \yD \yI) \approx \yFFm_{\yA_{t}}.
\end{equation}
The maximum-entropy distribution is exactly this mode $\yFm$, for
\emph{particular} kinds of probability densities $\pf(\yF \| \yD \yI)$
which we'll discuss shortly. Formulae~\eqref{eq:approx_delta_pF}
and~\eqref{eq:approx_delta_pA} show why the maximum-entropy distribution is
an approximate answer to two different questions.

@@

\textbullet\ The density $\exp[-\yL\;\ysh(\yF;\yR)]$ expresses our pre-data
uncertainty about the possible frequency distributions. Here
$\ysh(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\ln(\yFF_{\yA}/\yRR_{\yA})$ is the
relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is a
reference distribution, and $\yL$ a positive parameter. This density
expresses a belief proportional to the number of ways in which the
frequency distribution $\yF$ can be realized if we assume that the
activities appear with frequencies $\yR$ in the long run, as can be seen
using Stirling's approximation. For $\yR$ we choose the uniform
distribution, but any biologically sensible distribution, such as one
decreasing exponentially with the activity, leads to the same final
results. The parameter $\yL$ roughly represents the number of data points
necessary to change our initial belief, and we set it equal to $50$. This
density is similar to an \enquote{entropic prior}
\citep{rodriguez1991,skilling1998,catichaetal2004,portamana2017}[see
esp.][\sect~3]{neumann2007}.

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T13:29:31+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Now consider the related question: What is the activity $\yA_{t}$ of the
full network at some specific time bin $t$? If we don't know the exact
sequence of activities during the recording then we don't know $\yA_{t}$;
if we know the frequency distribution $\yF$ of the activity levels, then
our probability for $\yA_{t}$ is $\yFF_{\yA_{t}}$, out of combinatorial
reasons. But if we are also uncertain about $\yF$, with
probability~\eqref{eq:density_F}, then our probability for $\yA_{t}$ by
marginalization is
\begin{equation}
  \label{eq:probability_AT}
  \pf(\yA_{t} \| \yD \yI) =
  \int \yFF_{\yA_{t}}\;   \pf(\yF \| \yD \yI)\;\di\yF;
\end{equation}
our probability distribution for $\yA_{t}$ is thus simply the mean
$\int \yF\; \pf(\yF \| \yD \yI)\;\di\yF$.

@@

If the probability density $\pf(\yF \| \yD \yI)$ is extremely peaked at some
frequency distribution $\yFm$, it can be approximately treated as a delta
density,
\begin{equation}
  \label{eq:approx_delta_pF}
  \pf(\yF \| \yD \yI)\;\di\yF \approx \delt(\yF-\yFm)\;\di\yF,
\end{equation}
and consequently the probability for the activity at bin $t$, by
\eqn~\eqref{eq:probability_AT}, is simply the mode $\yFm$ itself:
\begin{equation}
  \label{eq:approx_delta_pA}
  \pf(\yA_{t} \| \yD \yI) \approx \yFFm_{\yA_{t}}.
\end{equation}
The maximum-entropy distribution is exactly this mode $\yFm$, for
\emph{particular} kinds of probability densities $\pf(\yF \| \yD \yI)$
which we'll discuss shortly. Formulae~\eqref{eq:approx_delta_pF}
and~\eqref{eq:approx_delta_pA} show why the maximum-entropy distribution is
an approximate answer to two different questions.

@@

\textbullet\ The density
\begin{equation}
\exp[-\yL\;\ysh(\yF;\yR)]\label{eq:entropic_prior}
\end{equation}
expresses our pre-data
uncertainty about the possible frequency distributions. Here
$\ysh(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\ln(\yFF_{\yA}/\yRR_{\yA})$ is the
relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is a
reference distribution, and $\yL$ a positive parameter. This density
expresses a belief proportional to the number of ways in which the
frequency distribution $\yF$ can be realized if we assume that the
activities appear with frequencies $\yR$ in the long run, as can be seen
using Stirling's approximation. For $\yR$ we choose the uniform
distribution, but any biologically sensible distribution, such as one
decreasing exponentially with the activity, leads to the same final
results. The parameter $\yL$ roughly represents the number of data points
necessary to change our initial belief, and we set it equal to $50$. This
density is similar to an \enquote{entropic prior}
\citep{rodriguez1991,skilling1998,catichaetal2004,portamana2017}[see
esp.][\sect~3]{neumann2007}.

@@

The post-data belief density~\eqref{eq:density_proportional} has a
maximum-entropy distribution as a mode approximation when $\ycs$ is small,
$\yL$ is large, and $\ycs L$ is small. Its mode in fact will be the
constrained $\yF$ that maximizes the relative entropy $\ysh(\yF;\yR)$. It
should be noted that a pre-data belief different from the entropic
one~\eqref{eq:entropic_prior} will lead to a different mode approximation.
For example, a Dirichlet density would lead to a maximum-entropy
distribution with \emph{Burg's} entropy \citey{burg1975} instead of
Shannon's \citep{jaynes1986d_r1996}.
